Project Plan for \texttt{timeline}: a Time Series Visualization Platform

### 2016-04-29 docs/projectplan/projectplan.tex
some minor changes in the project plan

\author{Manuel Haid (1131404) \\ Thomas Mauerhofer (1031957) \\ Matthias Wölbitsch (1130899) \\ \\ Group 001}
\title{Project Plan for \texttt{timeline}: a Time Series Visualization Framework}
\date{}

@@

When dealing with time series usually one of the first steps in the analysis process is the visualization of the data.
The graphical representation can already give some great insights in properties of the data.
For example, a simple visual inspection can show patterns, trends or seasonal effects without the use of advanced statistical methods. 
These properties are important since they have to be considered in the modeling of the time series (e.g. in forecasting models).
The goal of our project is to create a web-based framework that allows the user to perform this initial visual inspection of the time series in a convenient but sophisticated way.

@@

The time series visualization framework mainly consists of of a front-end and a back-end part.
This architectural design choice implies a clear separation of concerns. 
The back-end will be implemented in Python and is used for the processing of the data while the HTML/JavaScript front-end is used to present different views to the user.

@@

The front-end of the application is a simple HTML5 website that uses a JavaScript visualization library to display the visualization primitives.
Which JavaScript visualization library will be used was not decided yet.
However, a little bit of research showed that there plenty of different libraries available that support the plotting of temporal data.
For example, two time series visualization libraries that are based on the well-known D3.js libary are Cubism.js and MetricsGraphics.js could be used for this project.
Currently we plan to support the following visualization primitives which can be generated by the visualization engine and rendered by the front-end:

>>>>

\author{Manuel Haid (1131404) \\ Thomas Mauerhofer (1031957) \\ Matthias Wölbitsch (1130899) \\ \\ Group 001}
\title{Project Plan for \texttt{timeline}: a Time Series Visualization Platform}
\date{}

@@

When dealing with time series usually one of the first steps in the analysis process is the visualization of the data.
The graphical representation can already give some great insights in properties of the data.
For example, a simple visual inspection can show patterns, trends or seasonal effects without the use of advanced statistical methods. 
These properties are important since they have to be considered in the modeling of the time series (e.g. in forecasting models).
The goal of our project is to create a web-based platform that allows the user to perform this initial visual inspection of the time series in a convenient but sophisticated way.

@@

The time series visualization platform mainly consists of of a front-end and a back-end part.
This architectural design choice implies a clear separation of concerns. 
The back-end will be implemented in Python and is used for the processing of the data while the HTML/JavaScript front-end is used to present different views to the user.

@@

The front-end of the application is a simple HTML5 website that uses a JavaScript visualization library to display the visualization primitives.
Which library will be used was not decided yet.
However, a little bit of research showed that there plenty of different libraries available that support the plotting of temporal data.
For example, two time series visualization libraries, that are based on the well-known D3.js libary, are Cubism.js and MetricsGraphics.js could be used for this project.
Currently we plan to support the following visualization primitives which can be generated by the visualization engine and rendered by the front-end:
